Motional Ground State Cooling Outside the Lamb-Dicke Regime

### 2018-01-29 paper.tex
Disable decoherence term for non axial heating sideband to match what we say in the paper

\begin{figure*}
  \includegraphics[height=4.2cm]{spectrum_r.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_rx_0.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_rx_p1.pdf}
  \caption{(A) Left to right: Radial Raman sideband spectrum of $\Delta n_y=1,\,\Delta n_x=1,\,\Delta n_x=-1,\,\Delta n_y=-1,\,\Delta n_x=-2,\,\Delta n_y=-2$ before and after Raman sideband cooling.
    (B,C) Rabi flopping on axis $x$ (B) carrier and (C) $\Delta n_x=1$ sideband
    before (red circle) and after (blue square) RSC.
    Solid lines in (B) and (C) are fits to a Rabi-flopping
    that includes a thermal distribution of motional states~\cite{Meekhof1996}
    as well as off-resonant scattering from the Raman beams.
    The blue lines correspond to a 1D ground state probability of $98.1$\% after cooling
    and the red lines correspond to a thermal distribution of $80$ $\mu$K before RSC.
    \label{f-radial}}
\end{figure*}
\begin{figure*}
  \includegraphics[height=4.2cm]{spectrum_az.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_az_0.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_az_p1.pdf}
  \caption{(A) Left to right: Axial Raman sideband spectrum from $\Delta n_z=1,0,-1,\ldots,-5$
    before and after Raman sideband cooling.
    (B,C) Rabi flopping on axial (B) carrier $\Delta n_z=0$  and (C) $\Delta n_z=1$ sideband
    before (red circle) and after (blue square) RSC.
    Solid blue lines in (B) and (C), similar to Fig.~\ref{f-radial}B and C,
    are fits to the Rabi flopping and yield a ground state probability of $95$\%
    after cooling and
    the red lines correspond to a thermal distribution of $80$ $\mu$K before RSC.
    The green line in (C), includes the additional decoherence due to
    a fluctuation of the hyperfine splitting of magnitude $3$ kHz.
    We see that the decoherence effect is strongest for the post-cooling data on
    the $\Delta n_z=1$ sideband where the Rabi frequency is the lowest.
    \label{f-axial}}
\end{figure*}

>>>>

\begin{figure*}
  \includegraphics[height=4.2cm]{spectrum_r.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_rx_0.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_rx_p1.pdf}
  \caption{(A,B) Left to right: Radial Raman sideband spectrum of $\Delta n=1,\,\Delta n=0,\,\Delta n=-1,\,\Delta n=-2$ before and after Raman sideband cooling for $x$ and $y$ axis.
    (C,D) Rabi flopping on axis $x$ (B) carrier and (C) $\Delta n_x=1$ sideband
    before (red circle) and after (blue square) RSC.
    Solid lines in (C) and (D) are fits to a Rabi-flopping
    that includes a thermal distribution of motional states~\cite{Meekhof1996}
    as well as off-resonant scattering from the Raman beams.
    The blue lines correspond to a 1D ground state probability of $98.1$\% after cooling
    and the red lines correspond to a thermal distribution of $80$ $\mu$K before RSC.
    \label{f-radial}}
\end{figure*}
\begin{figure*}
  \includegraphics[height=4.2cm]{spectrum_az.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_az_0.pdf}
  \includegraphics[height=4.2cm]{rabi_flop_az_p1.pdf}
  \caption{(A) Left to right: Axial Raman sideband spectrum from $\Delta n_z=1,0,-1,\ldots,-5$
    before and after Raman sideband cooling.
    (B,C) Rabi flopping on axial (B) carrier $\Delta n_z=0$  and (C) $\Delta n_z=1$ sideband
    before (red circle) and after (blue square) RSC.
    Solid blue lines in (B) and (C), similar to Fig.~\ref{f-radial}B and C,
    are fits to the Rabi flopping and yield a ground state probability of $95$\%
    after cooling and
    the red lines correspond to a thermal distribution of $80$ $\mu$K before RSC.
    The green line in (C), includes the additional decoherence due to
    a fluctuation of the hyperfine splitting of magnitude $3$ kHz.
    We see that the decoherence effect is strongest for the post-cooling data on
    the $\Delta n_z=1$ sideband where the Rabi frequency is the lowest.
    \label{f-axial}}
\end{figure*}
